Lasso_RCI_Response

### 2024-03-17 Lasso_RCI_Response.Rmd
Changed to JT plot/classification

          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1,

@@

summary(Mothership$Co_Anx)
table(Mothership$Anxiety_D, Mothership$Co_Anx)
##### df for plots

@@

DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")

RCI_DF<- ANX_RCI$data
colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")

@@

@@

#2. Left join data from the RCI dataset into the Mothership_post df
Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    )),
    RESPONDER_FIGS = as.factor(
      ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
             ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
      ))) |>
  filter(!is.na(RESPONDER_FIGS))

#############            AnxDep_PrePost                 ##################

@@

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                   Mothership_post$Disorder_treat,
                                   Mothership_post$BL_CUDOS,
                                   Mothership_post$BL_CUXOS,
                                   Mothership_post$CUDOS_pre,
                                   Mothership_post$CUDOS_post,
                                   Mothership_post$CUXOS_pre,
                                   Mothership_post$CUXOS_post,
                                   #Extra stuff?
                                   Mothership_post$Depression_Responder,
                                   Mothership_post$Anxiety_Responder,
                                   Mothership_post$RESPONDER_FIGS
)) #%>%
#filter(!is.na(Mothership_post$Disorder_treat))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
                             "Anxiety_Responder", "RESPONDER_FIGS")

@@

summary(Mothership_lasso$Depression_Responder)

@@

#3. Get statistics for variables + Assign to table
  # Anxiety - CUXOS
    #make df
      anx_rep_tab <- Mothership_post |>
        group_by(Anxiety_Responder) |>
        summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
                  pre_anx_sd = round(sd(CUXOS_pre, na.rm = TRUE),2),
                  post_anx = round( mean(CUXOS_post,na.rm = TRUE),2),
                  post_anx_sd = round( sd(CUXOS_post,na.rm = TRUE),2),
                  delta_anx = round( mean(Delta_Anx_DC,na.rm = TRUE),2),
                  delta_anx_sd = round( sd(Delta_Anx_DC, na.rm = TRUE),2)
                  )
# add to scores tab
        Scores_tab[2,] = c(
          "CUXOS",
          #Non-responder scores
          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")"),
          #responder scores
          paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
          paste0(anx_rep_tab$post_anx[[1]]," (",anx_rep_tab$post_anx_sd[[1]],")"),
          paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
          20,
          20
        )

# Depression - CUDOS
  #Make df
    dep_rep_tab <- Mothership_post |>
      group_by(Depression_Responder) |>
      summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
                pre_dep_sd = round( sd(CUDOS_pre, na.rm = TRUE),2),
                post_dep = round( mean(CUDOS_post, na.rm = TRUE),2),
                post_dep_sd = round( sd(CUDOS_post, na.rm = TRUE),2),
                delta_dep = round( mean(Delta_Dep_DC, na.rm = TRUE),2),
                delta_dep_sd = round( sd(Delta_Dep_DC, na.rm = TRUE),2)
                )
    #Add to Scores_tab
       Scores_tab[3,] = c(
        "CUDOS",
        #Non-responder scores
        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")"),
        #responder scores
        paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
        paste0(dep_rep_tab$post_dep[[1]]," (",dep_rep_tab$post_dep_sd[[1]],")"),
        paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
        20,
        13
      )

@@

Figure 1: Pre-post Line Plot
```{r}
#### Redo and recreate dataset for Anxiety or depression response.
AnxDep_response_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(RESPONDER_FIGS)) |>
  group_by(Test,RESPONDER_FIGS,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

ggplot(data=AnxDep_response_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
      c("1" = "Non-Responders", 
        "2" = "Responders")
      ))
```

### Disorder Breakdowns
Here are some tables displaying info on the psychiatric disorders treated at the PHP
```{r}
# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
                                     data = Mothership_post))
colnames(Dis_tab) = c("Variables","Non Responder", "Responder", "Total")
Dis_tab

@@

co_dis_tab <- Mothership_post |>
  filter(
      !is.na(rdq_func_change),
      !is.na(rdq_pmh_change),
      !is.na(rdq_coping_change),
      !is.na(rdq_wbs_change)
  ) |>
  pivot_longer(
    cols = c("Anxiety_C","Mood_C","BPD_Co_C","Other_C", "Substance_C","Trauma_C", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat),
         )

@@

Figure 1: Pre-post Line Plot
```{r}

AnxDep_response_mean<-AnxDep_PrePost_Long %>%
  filter(!is.na(RESPONDER_FIGS)) |>
  group_by(Test,RESPONDER_FIGS,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))

ggplot(data=AnxDep_response_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
      c("1" = "Non-Responders", 
        "2" = "Responders")
      ))
```

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
Vars_dep <- Mothership_post |>
  select( c(
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

str(Vars_dep)

Vars_anx <- Mothership_post |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

@@

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}

RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
#anxiety

RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
# Depresssion
RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
# #Total
# RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])

RCI_table
```

@@

# Depression Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_dep <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder)
  )

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

#The exact value of lambda can be viewed as follow:
print(paste0("This is the minimum lambda value: ", round(cv.lasso.dep$lambda.min,5)))

#This value is called lambda.1se.
print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso.dep$lambda.1se,5)))

@@

# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

@@

Evaluating if we should use Lasso min or 1SE- Depression
```{r}
####  Using Min
# Final model with lambda.min
lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.min)

@@

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.1se)
coef(lasso.model.1se.dep)
# Make prediction on test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.dep %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

@@

```{r}
## min model
  glm_min_dep <-
      glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        White + Days_complete_1 + Days_not_attended_1 + Mood_D + Substance_D + 
        Other + Anxiety_C + Mood_C + Substance_C + CUDOS_pre + CUXOS_pre + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

# Anxiety Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_anx <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder)
  )

>>>>

          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 |
            Schiz_P == 1 | Schizaff_P == 1 |
              Alcohol_P == 1 | Drug_P ==1,

@@

##### df for plots

@@

## Using RCI only (respond/nonrespond/deteriorated)
DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

ANX_RCI <- JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")
RCI_DF<- ANX_RCI$data
colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")

@@

```{r}
#Using JT citeria (recovered/improved/nonresponse/deteriorated)

#1. JT classification for depression
JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  JTcrit = "auto",
                  plottitle = "JT indices for anxiety")

DEP_JT <- JTRCIdf

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  #JTcrit = "auto",
                  plottitle = "JT indices for depression")

ANX_JT<- JTRCIdf

#3. Make combined JT table for anxiety and depression

JT_DF<- ANX_JT

colnames(JT_DF) <- paste0(colnames(JT_DF),"_anx")

JT_DF2<- DEP_JT
colnames(JT_DF2) <- paste0(colnames(JT_DF2),"_dep")

JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
colnames(JT_DF)[1] = "ID1"

JT_DF

@@

#2. Left join data from the RCI dataset into the Mothership_post df
# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
#   mutate(
#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "1" = "2",
#                                             "2" = "2",
#                                             "3" = "1"
#     )),
#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "2" = "Non-Responder",
#                                             "1" = "Responder"
#     )),
#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "1" = "2",
#                                          "2" = "2",
#                                          "3" = "1"
#     )),
#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "2" = "Non-Responder",
#                                          "1" = "Responder"
#     )),
#     RESPONDER_FIGS = as.factor(
#       ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
#              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
#       ))) |>
#   filter(!is.na(RESPONDER_FIGS))

Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder)
    )
```

```{r}
#############            AnxDep_PrePost                 ##################

@@

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                   Mothership_post$Disorder_treat,
                                   Mothership_post$BL_CUDOS,
                                   Mothership_post$BL_CUXOS,
                                   Mothership_post$CUDOS_pre,
                                   Mothership_post$CUDOS_post,
                                   Mothership_post$CUXOS_pre,
                                   Mothership_post$CUXOS_post,
                                   #Extra stuff?
                                   Mothership_post$Depression_Responder,
                                   Mothership_post$Anxiety_Responder
                                   #Mothership_post$RESPONDER_FIGS
)) #%>%
#filter(!is.na(Mothership_post$Disorder_treat))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
                             "Anxiety_Responder")
#, "RESPONDER_FIGS")

@@

@@

#3. Get statistics for variables + Assign to table
  # Anxiety - CUXOS
    #make df
      anx_rep_tab <- Mothership_lasso |>
        group_by(Anxiety_Responder) |>
        summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
                  pre_anx_sd = round(sd(CUXOS_pre, na.rm = TRUE),2),
                  post_anx = round( mean(CUXOS_post,na.rm = TRUE),2),
                  post_anx_sd = round( sd(CUXOS_post,na.rm = TRUE),2),
                  delta_anx = round( mean(Delta_Anx_DC,na.rm = TRUE),2),
                  delta_anx_sd = round( sd(Delta_Anx_DC, na.rm = TRUE),2)
                  )
# add to scores tab
        Scores_tab[2,] = c(
          "CUXOS",
          #Non-responder scores
          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")"),
          #responder scores
          paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
          paste0(anx_rep_tab$post_anx[[1]]," (",anx_rep_tab$post_anx_sd[[1]],")"),
          paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
          20,
          20
        )

# Depression - CUDOS
  #Make df
    dep_rep_tab <- Mothership_lasso |>
      group_by(Depression_Responder) |>
      summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
                pre_dep_sd = round( sd(CUDOS_pre, na.rm = TRUE),2),
                post_dep = round( mean(CUDOS_post, na.rm = TRUE),2),
                post_dep_sd = round( sd(CUDOS_post, na.rm = TRUE),2),
                delta_dep = round( mean(Delta_Dep_DC, na.rm = TRUE),2),
                delta_dep_sd = round( sd(Delta_Dep_DC, na.rm = TRUE),2)
                )
    #Add to Scores_tab
       Scores_tab[3,] = c(
        "CUDOS",
        #Non-responder scores
        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")"),
        #responder scores
        paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
        paste0(dep_rep_tab$post_dep[[1]]," (",dep_rep_tab$post_dep_sd[[1]],")"),
        paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
        20,
        13
      )

@@

Figure 1: Pre-post Line Plot
```{r}
#1. Create long data frame for pre/post depression
dep_prepost <- dep_rep_tab |>
  pivot_longer(
    cols = c("pre_dep", "post_dep"),
    names_to = "PrePost",
    values_to = "Score"
  ) |>
  select(Depression_Responder,PrePost,Score) |>
  mutate(
    Test = "CUDOS",
    PrePost = ifelse(PrePost == "pre_dep", "Pre", "Post")
  )
colnames(dep_prepost)[1] = "Responder"

#2. Create long data frame for pre/post anxiety
anx_prepost <- anx_rep_tab |>
  pivot_longer(
    cols = c("pre_anx", "post_anx"),
    names_to = "PrePost",
    values_to = "Score"
  ) |>
  select(Anxiety_Responder,PrePost,Score) |>
  mutate(
    Test = "CUXOS",
    PrePost = ifelse(PrePost == "pre_anx", "Pre", "Post"),
  )
colnames(anx_prepost)[1] = "Responder"

#3. Combine dataset
AnxDep_fig_response <- rbind(dep_prepost,anx_prepost)

#4. Plot pre post scores by treatment response
ggplot(data=AnxDep_fig_response,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=fct_rev(Test)))+
  geom_point(size=2.5) +
  geom_line(group=AnxDep_fig_response$PrePost,size=1.5)+
  ### ADD confidience intervals??
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_wrap(~Responder)
```

### Disorder Breakdowns
Here are some tables displaying info on the psychiatric disorders treated at the PHP
```{r}
# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Anxiety_Responder, 
                                     data = Mothership_lasso))
colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")

Dis_tab1 <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Depression_Responder, 
                                     data = Mothership_lasso))
colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
Dis_tab

@@

co_dis_tab <- Mothership_lasso |>
  filter(
      !is.na(rdq_func_change),
      !is.na(rdq_pmh_change),
      !is.na(rdq_coping_change),
      !is.na(rdq_wbs_change)
  ) |>
  pivot_longer(
    cols = c("Anxiety_C","Mood_C","BPD_Co_C","Other_C", "Substance_C","Trauma_C", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat),
         )

@@

Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
# Vars_dep <- Mothership_post |>
#   select( c(
#     # Demographics
#     Age_1,Some_College:Married,White, #Discharge,
#     # Treatment info
#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
#     # Disorders
#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,
#     # Pre-Post stuff
#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
#     # RDQ
#     rdq_coping_change:rdq_wbs_change
#   ))
# 
# str(Vars_dep)
# 
# Vars_anx <- Mothership_post |>
#   select( c(
#     Anxiety_Responder,
#     # Demographics
#     Age_1,Some_College:Married,White, #Discharge,
#     # Treatment info
#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
#     # Disorders
#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,
#     # Pre-Post stuff
#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
#     # RDQ
#     rdq_coping_change:rdq_wbs_change
#   ))

@@

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}
# RCI STUFF
# RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
# colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
# #anxiety 
# 
# RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
# # Depresssion
# RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
# # #Total
# # RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
# 
# RCI_table

# JT Table
JT_table <- data.frame(matrix(NA,nrow = 2,ncol = 3))
colnames(JT_table) = c("Varaibles","Responder","Non-Responder")
#anxiety

JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
# Depresssion
JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))

JT_table
```

@@

# Depression Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_dep <- Mothership_lasso |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder)
  )

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

#The exact value of lambda can be viewed as follow:
print(paste0("The minimum lambda value is: ", round(cv.lasso.dep$lambda.min,5)))

#This value is called lambda.1se.
print(paste0("The 1 standard error lambda value is: ", round(cv.lasso.dep$lambda.1se,5)))

@@

# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model.min %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

@@

Evaluating if we should use Lasso min or 1SE- Depression
```{r}
####  Using Min
# Final model with lambda.min
lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso.dep$lambda.min)

@@

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso.dep$lambda.1se)
coef(lasso.model.1se.dep)
# Make prediction on test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.dep %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

@@

```{r}
## min model
  glm_min_dep <-
      glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +  
        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

# Anxiety Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_anx <- Mothership_lasso |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder)
  )

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
    Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))
